Population structure and phenotypic variation of *Sclerotinia sclerotiorum* from dry bean throughout the United States, and from Mexico, France, and Australia

### 2017-06-29 doc/manuscript/manuscript.Rmd
Add table 1 to manuscript

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or dry bean nurseries in Mexico, France, Australia, and 11 states of the United States of America (Table 1).
The dry bean nurseries in different regions are indicated by wmn (white mold nursery) or mtc (Mitchell) and all other isolates came from commercial fields (Table 1).
The bean nurseries were 5m x 10 m in size and maintained without applying fungicides to observe natural incidence of white mold disease.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the season.
Although the nursery locations were the same over sampling years, sampling fields within a location varied for sampling years.
Sampling was carried out on a 'W' or 'V' shape transect, or randomly.
Sampling year and number of isolates collected were necessarily influenced by incidence and severity of white mold disease.

>>>>

Sclerotia of *S. sclerotiorum* were collected over several years from grower fields and/or dry bean nurseries in Mexico, France, Australia, and 11 states of the United States of America (Table \@ref(tab:isolate-table)).
The dry bean nurseries in different regions are indicated by wmn (white mold nursery) or mtc (Mitchell) and all other isolates came from commercial fields (Table \@ref(tab:isolate-table)).
The bean nurseries were 5m x 10 m in size and maintained without applying fungicides to observe natural incidence of white mold disease.
The nursery plots were incorporated with a basal dressing of N:P:K = 1:3:2 and side dressing of 0:3:2 during the season.
Although the nursery locations were the same over sampling years, sampling fields within a location varied for sampling years.
Sampling was carried out on a 'W' or 'V' shape transect, or randomly.
Sampling year and number of isolates collected were necessarily influenced by incidence and severity of white mold disease.

-----------------------------------------------------------------------------
Country   State  Field Code              Year Host                          N 
--------- ------ ---------- ----------------- -------------------------- ----
USA       CA     wmn               2004, 2005 Beryl, Bunsi, G122           18

USA       CO     eat               2007, 2010 Yellow                       13

                 gree              2007, 2010 Pinto, Yellow                14

                 luc               2007, 2010 Yellow                       14

                 wmn                     2003 GH                            1

USA       ID     unk                     2003 GH                            1

USA       MI     eln                     2009 unk                           1

                 hur               2008, 2009 BL, Black, SR06233, Vista     5

                 mung                    2009 Zorro                         1

                 sanc                    2008 Merlot                        3

                 Sebewaing               2009 Black                         1

                 tuc               2008, 2009 Black, Fuji, Vista            6

                 unk               2003, 2009 GH, unk                       2

                 wmn        2003, 2004, 2005, 11A, 37, 38, B07104,         43 
                                   2008, 2009 Beryl, Bunsi, cornell,          
                                              G122, Orion, PO7863, WM31

USA       MN     wmn               2003, 2004 Beryl, Bunsi, G122           11

USA       ND     gfc               2007, 2010 unk                           9

                 nec                     2010 unk                           1

                 pmc                     2010 unk                           7

                 rrv                     2007 unk                          21

                 stc                     2010 unk                           2

                 tlc                     2010 unk                           9

                 wlc                     2010 unk                           4

                 wmn                     2005 Beryl, Bunsi, G122            7

USA       NE     mtc               2007, 2010 Beryl, Emerson, Orion        12

                 sbf               2007, 2009 Beryl, Pinto, Weihing         6

                 unk                     2003 GH                            2

                 wmn        2004, 2005, 2008, Beryl, Bunsi, G122,          27 
                                         2010 PO7683, unk

USA       NY     unk                     2003 GH                            1

USA       OR     corv                    2003 G122                          1

                 unk                     2003 GH                            1

                 wmn               2003, 2004 Beryl, Bunsi, G122           15

USA       WA     prsr                    2007 Merlot, Pinto, redkid        22

                 unk                     2003 GH                            1

                 wmn        2003, 2004, 2005, 11A, 37, 38, Beryl, Bunsi,   36 
                                         2008 cornell, G122, Orion,           
                                              PO7104, PO7863, WM31

USA       WI     dfor                    2003 GH                            1

                 unk                     2003 GH                            1

Mexico           wmn                     2005 Beryl, Bunsi, G122           18

France           flds                    2012 unk                           4

                 wmn               2004, 2005 Beryl, Bunsi, G122           18

Australia        vic                     2004 Beryl                         2

                 wmn                     2004 Beryl, Bunsi, G122            4

-----------------------------------------------------------------------------

Table: (\#tab:isolate-table) Description of *S. sclerotiorum* isolates used in this study. 
N = Number of Isolates. 
Key abbreviations: wmn = white mold nursery, unk = unknown.
